\section{Data}\label{sec:data}

\subsection{Source}\label{sec:data:source}

The dataset is produced by PHREEQC version~3, driven by the
\texttt{phreeqc.dat} thermodynamic database and a custom kinetic
model file (\texttt{model\_v23.phr}). $N = 1000$ runs are generated;
the database and the model file are identical across runs.

\subsection{Per-run sampling}\label{sec:data:knobs}

Each run is parameterised by $24$ input entries, four of which are
sampled independently per run (\cref{tab:data:knobs}). Three of the
four -- \texttt{ALKALINITY}, \texttt{CARBONDIOXIDE},
\texttt{HYDROGEN\_SULFIDE} -- are scaled by an independent draw from
$U(0.5, 1.5)$ around their default. The fourth, \texttt{QUARTZ},
drives a cascade that partitions a fixed total rock mass
$M_{\text{rock}} = 0.1$\,kg across the five mineral phases:
\begin{align}
m_{\text{Qz}}    &= M_{\text{rock}} \cdot u_1, \quad u_1 \sim U(0.65, 0.95) \label{eq:rock:qz} \\
m_{\text{Cal}}   &= (M_{\text{rock}} - m_{\text{Qz}}) \cdot u_2, \quad u_2 \sim U(0.30, 0.80) \label{eq:rock:cal} \\
m_{\text{Py}} = m_{\text{Ba}} = m_{\text{Il}}
                 &= \tfrac{1}{3}\bigl(M_{\text{rock}} - m_{\text{Qz}} - m_{\text{Cal}}\bigr). \label{eq:rock:rest}
\end{align}
The total rock mass is conserved at $0.1$\,kg in every run.

\begin{table}[ht]
  \centering
  \caption{The four input variables sampled per run. The first three
  are scaled by an independent draw from $U(0.5, 1.5)$;
  \texttt{QUARTZ} drives the rock partition in
  \cref{eq:rock:qz,eq:rock:cal,eq:rock:rest}.}
  \label{tab:data:knobs}
  \begin{tabular}{llll}
    \toprule
    Variable & Default & Range & Unit \\
    \midrule
    \texttt{ALKALINITY}        & $4.90\times10^{-3}$ & $[2.45,\,7.35]\times10^{-3}$ & mol/kgw \\
    \texttt{CARBONDIOXIDE}     & $2.9$               & $[1.45,\,4.35]$              & atm \\
    \texttt{HYDROGEN\_SULFIDE} & $4\times10^{-3}$    & $[2,\,6]\times10^{-3}$       & atm \\
    \texttt{QUARTZ}            & --- (cascade)        & see \cref{eq:rock:qz}        & kg \\
    \bottomrule
  \end{tabular}
\end{table}

The remaining ten species (sodium, potassium, magnesium, chloride,
iron, sulfur, calcium, formate, methane, hydrogen) are held at their
default values, and acetate is forced to $1\times10^{-6}$. Across all
$1000$ runs these eleven entries are byte-identical.

\subsection{Derived per-mineral quantities}\label{sec:data:derived}

For each mineral, an initial mole count $n$ and a reactive surface
area $A$ are derived from the per-run mass $m$ and three constants --
molecular weight $M$, particle diameter $d$, and density $\rho$
(\cref{tab:data:minprops}):
\begin{equation}\label{eq:mol-area}
  n = \frac{1000\,m}{M}, \qquad A = \frac{6\,m}{\rho\,d}.
\end{equation}
The factor $1000$ converts $m$ from kg to g. The surface-area
expression assumes spherical particles. The triple $(M, d, \rho)$ is
constant across runs.

\begin{table}[ht]
  \centering
  \caption{Mineral constants used in \cref{eq:mol-area}.}
  \label{tab:data:minprops}
  \begin{tabular}{lrrr}
    \toprule
    Mineral & $M$ (g/mol) & $d$ ($\mu$m) & $\rho$ (kg/m$^3$) \\
    \midrule
    Quartz  &  60 & 200 & 2650 \\
    Calcite & 100 & 100 & 2710 \\
    Pyrite  & 120 &  10 & 5000 \\
    Barite  & 234 &  10 & 4500 \\
    Illite  & 390 &   1 & 2700 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Output structure}\label{sec:data:out}

For each run, PHREEQC writes a tabular text file with one header row
and $101$ data rows. Simulated time advances $96$ days in $100$ equal
steps, so $\Delta t = 0.96$\,d ($\approx 23$\,h). Row~$1$ records the
state at $t = 0$; rows $2$--$101$ record the state after each
integration step. Each row contains $13$ columns:
\texttt{time\_d}, \texttt{pH}, \texttt{Ptot\_atm}, \texttt{pH2\_atm},
\texttt{pCO2\_atm}, \texttt{pCH4\_atm}, \texttt{CH4\_g\_mol},
\texttt{H2\_g\_mol}, \texttt{CO2\_g\_mol}, \texttt{SO4},
\texttt{Formate}, \texttt{Acetate}, \texttt{Ca}.

The transition between row~$1$ and row~$2$ is not a smooth dynamic
step. The user-specified initial conditions are echoed verbatim at
$t = 0$, and the gas phase is equilibrated only during the first
integration step. In run~$1$, for instance, \texttt{Ptot\_atm} jumps
from $2.34$ to $79.84$\,atm and \texttt{pH2\_atm} from $0$ to
$9.10$\,atm across that single step. The downstream pipeline
therefore treats row~$2$ ($t = 0.96$\,d) as the effective starting
state and drops row~$1$.
